Three objections to a novel person-specific paradigm in social media effects research

### 2022-07-14 ms.Rmd
Revision

---
title: Three objections to a novel person-specific paradigm in social media effects research
shorttitle: Three objections
leftheader: Three objections
author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes    # Define only one corresponding author
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - Conceptualization
      - Formal analysis
      - Software
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name: Niklas Johannes
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: niklas.johannes@oii.ox.ac.uk
    role:
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name: Andrew K. Przybylski
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: andy.przybylski@oii.ox.ac.uk
    role:
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
affiliation:
  - id: 1
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  A non-peer reviewed pre-print of this work is available at <psyarxiv>.
  All code supporting this manuscript is available at <github>.
abstract: |
  The study of social media effects on psychological well-being has reached an impasse: Popular commentators "know" that social media are bad for you but research results are mixed and have had little practical impact. In response, one research group aims to move beyond studying population averages to find effects that are specific to individuals.

  Here, we outline three objections to that research programme. On a methodological level, the key empirical results of this programme---proportions of the population of individuals with negative, null, and positive social media effects---are inappropriately estimated and reported. On a theoretical level, these results do little to advance our understanding of social media and its psychological implications. On a  paradigmatic level, this "personalized media effects paradigm" [@valkenburgSocialMediaUse2021, p.74] does not make inferences about individuals and therefore does not deliver what it claims.

  We fear that this research programme is contributing to confusing messaging to both societal stakeholders and scientists. We hope that describing these objections will prompt the field to work together in adopting better practices to ultimately develop a better understanding of well-being in the digital age.
keywords: social media, media effects, well-being, variation, paradigm
wordcount: "2,802"
bibliography: person-specific-paradigm.bib
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

@@

The main outcomes of the programme under question are "striking person-specific effects" [@valkenburgSocialMediaUse2022a, p.5]: Proportions of adolescents with negative, null, and positive associations between social media use and various well-being outcomes. We take these numerical results to be the key estimands because they are typically the numerical results reported in paper abstracts [e.g. @beyensSocialMediaUse2021; @valkenburgSocialMediaBrowsing2021]. Here, we suggest that those numbers are inappropriately calculated and interpreted.

@@

Thanks to the authors sharing their data [@Beyens2021], we reproduced their analysis in R, but with three key differences: We did not use robust standard errors, we were not able to reproduce the number of observations (authors reported 2,155, but the data we used had 2,210), and we focused on the arguably more meaningful unstandardized coefficients [@baguleyStandardizedSimpleEffect2009; @cohenProblemUnitsCircumstance1999; @moellerWordStandardizationLongitudinal2015]. In addition, we were not sure if the predictors were latent-mean or observed-mean centered. None of these differences are material to the points we are about to illustrate, but explain why the numbers we report do not exactly reproduce the numbers reported in [@beyensEffectSocialMedia2020]. We present the key parameter estimates from this model in Table \@ref(tab:tab-coef).

@@

We find these numbers problematic for two reasons. First, they are reported without considering the uncertainties in the person-specific estimates. We think that a person-specific approach, if it intends to make inferences about specific individuals, ought to consider the certainty with which those individuals' characteristics (i.e. person-specific effects) are estimated. Similarly, from a heterogeneity-perspective, ignoring uncertainties and making inferences based on point estimates only will lead to distorted results. Thus, a more suitable approach would be to find person-specific estimates that are outside the null region with (e.g.) 95% confidence [@kruschkeBayesianNewStatistics2017].

To illustrate this point, after estimating the model we drew a caterpillar plot of $(\bar\beta_1 + \beta_{1\text{person}[j]})$ and $(\bar\beta_2 + \beta_{2\text{person}[j]})$ (Figure \@ref(fig:caterpillar) left and right, respectively.) We colored the person-specific estimates based on whether the posterior mean was outside or inside the null region. The authors used standardized effect size limits of (-0.1, 0.1) for the null region, but here we used a smallest effect size of interest (SESOI) of (-0.14, 0.14) on the raw scale---an approximate magnitude of change required to subjectively notice changes on well-being scales of this type [@anvariUsingAnchorbasedMethods2021]. Only 1 out of 63 individuals in this sample had a credibly non-null estimated association between passive social media use and well-being (estimates that are credibly outside the null region are filled in Figure \@ref(fig:caterpillar)). No other person's parameter was credibly outside the null region. In fact, they all indicated indecisive, not null, results. We show these results numerically in the third column of Table \@ref(tab:tab-qoi). Ignoring the person-specific estimates' uncertainties can lead to numbers that do not represent the sample characteristics well, and can greatly articifially inflate the confidence in the results.

@@

x1 <- spread_draws(
  fit,
  b_active_c_w, b_passive_c_w,
  r_pid[pid, term] | term
) %>% 
  transmute(
    pid, .draw,
    Active = b_active_c_w + active_c_w,
    Passive = b_passive_c_w + passive_c_w
  ) %>% 
  pivot_longer(c(Active, Passive)) %>% 
  group_by(pid, name) %>% 
  mean_qi() %>% 
  mutate(
    zero = case_when(
      value >= 0.14 ~ "b",
      value <= -0.14 ~ "b",
      TRUE ~ "a"
    ),
    rope = case_when(
      .lower >= 0.14 ~ "Positive",
      .upper <= -0.14 ~ "Negative",
      .lower >= -0.14 & .upper <= 0.14 ~ "Null",
      TRUE ~ "Inconclusive"
    )
  ) %>% 
  arrange(name, value) %>% 
  mutate(pid = fct_inorder(str_c(pid, name)))
x1 %>% 
  ggplot(aes(value, pid, color = zero, shape = rope)) +
  scale_color_brewer(palette = "Paired") +
  scale_shape_manual(values = c(19, 21)) +
  geom_vline(xintercept = c(-.14, .14), lty = 2, size = .15) +
  geom_vline(xintercept = 0, lty = 1, size = .15) +
  scale_y_discrete(
    "Participant",
    expand = expansion(.025)
  ) +
  scale_x_continuous(
    "Estimated linear increase in well-being (1-7) as a\nfunction of a 10-minute increase in social media use",
    breaks = extended_breaks(7)
  ) +
  geom_linerange(
    size = .4,
    aes(xmin = .lower, xmax = .upper)
  ) +
  geom_point(fill = "white", stroke = 0.7, size = .9) +
  facet_wrap("name", scales = "free_y") +
  theme(
    axis.text.y = element_blank(), 
    axis.ticks.y = element_blank(),
    legend.position = "none"
  )
```

@@

For an illustration of calculating such population-level percentages, we again used a smallest effect size of interest (SESOI) of 0.14 on the raw scale. The results are shown in the fourth column of Table \@ref(tab:tab-qoi). Three lessons are immediate: One, the appropriately calculated percentages can be vastly different from those calculated from point estimates in Figure \@ref(fig:caterpillar). Two, calculating population-level quantities from the appropriate parameters allows quantifying uncertainty in them, as is shown in the credibility intervals of the percentages in Table \@ref(tab:tab-qoi). Three, there are no undecided person-specific parameters in the population, because the decision to accept or reject null hypotheses pertains to parameters at a different level of analysis. This last point highlights the confusion that results from how the programme under discussion here conflates studying heterogeneity (feature of the population) with person-specific effects (features of individual people), and therefore doesn't meaningfully contribute to an understanding of either.

@@

For these two reasons---ignoring uncertainties and confusing levels of analyses---we suggest that the percentages of social media associations in the population reported in (the abstracts of) a growing number of manuscripts from this research programme are misleading and lack critical context. We showed how those numbers can be appropriately calculated, and then presented with appropriate indications of uncertainty.

@@

Even if we calculate percentages correctly, how do we apply such information in developing and justifying a new paradigm? We argue that doing so is difficult and simply reporting that heterogeneity exists doesn't suffice. For one, the group interprets percentages that are not uniform as evidence that associations are not the same for everyone and we therefore cannot ignore heterogeneity. As we have said previously [@johannesHowShouldWe2021a]: So what---did any theory ever suggest as much? Variation is the norm, not the exception, and we consequently do not immediately know what to do with these findings. The authors suggest that because considerable and yet unexplained between-person differences seem to exist in social media associations, we therefore are now on the cusp of a personalized "media *effects* paradigm" [@valkenburgSocialMediaUse2021, p.74, emphasis ours] akin to those theorized for medicine and education. We argue that merely observing that variation might exist is an insufficient argument for the necessity of a new paradigm.

We are in agreement that when heterogeneity is considerable, our substantive statements about the population must be qualified by this variation [@bolgerCausalProcessesPsychology2019]. But this is not the same sentiment that drives the argument that we are discussing here. The intent, apparently, is to develop a personalized understanding of social media *effects* for each individual; a truly idiographic goal [@valkenburgSocialMediaUse2021, p.74]. However, to date this goal is approached by extrapolating from inappropriately calculated population-level quantities (percentages of individuals with associations in excess of some critical threshold). This fundamental tension between wants and haves has, we believe, led to a premature consideration of purportedly novel paradigms in a field that has not matured enough either methodologically or theoretically to consider addressing *causal* effects in this manner [see e.g. @ijzermanUseCautionWhen2020].

As we have argued [@johannesHowShouldWe2021a], one way to resolve this tension is to use the information gleaned about heterogeneity in considering meaningful moderators of social media associations [e.g. @bolgerCausalProcessesPsychology2019]. But this is standard practice in psychological research that routinely develops and refines theoretical models by moderating effects and associations with demographic and contextual variables. Another route, we believe espoused by this programme of research, is to move towards an idiographic (person-specific) research paradigm---a topic to which our next objection pertains.

@@

Throughout many papers, the group in question advertises their work as working toward or constituting a novel idiographic media effects paradigm [@valkenburgSocialMediaUse2022, p.66]. The argument goes that since they are conducting N=1 analyses, their conclusions are about individuals. But functions of ($\bar\beta_2$, $\sigma_{\beta_2}$) or poor stand-ins thereof (proportions of $\beta_2$), the main results reported in the manuscripts in question, are not idiographic in any meaningful sense of that research tradition. We think that to truly conduct N=1 analyses in an idiographic manner, one must do more than examine ranges of person-specific parameters.

In the context of multilevel models used in this body of work, idiographic research would refer to understanding each of 63 individuals' $\beta$s and what drove their differences.[^1] It seems to us an inescapable conclusion---unless one wants to conduct e.g. qualitative interview work which we should be doing anyway---that to study this heterogeneity further, we need to introduce more terms in our models to interact the associations of interest with meaningful contextual and person-level variables [@bolgerCausalProcessesPsychology2019]. These may then reduce the residual heterogeneity to such an extent that we may be excused to pronounce that a meaningful between-person moderator has been found, and we have learned something about individual differences in social media associations. Such conclusions and findings would be exceedingly difficult to come by through an idiographic-only approach, where individuals are "treated as holistic systems" [@howardVariableCenteredPersonCenteredPersonSpecific2018, p.849]. Repeating an earlier point, it is also important to not conflate person-specific analyses (which aim at analyzing a specific person) with effect heterogeneity (which encourages finding explanatory factors in the variation in effects).

[^1]: Prominent work in the idiographic research tradition actually argues against using shrinkage estimates for understanding individuals' characteristics, and as a consequence suggests that multilevel models are inappropriate tools for idiographic research [@molenaarManifestoPsychologyIdiographic2004; @molenaarNewPersonSpecificParadigm2009]. While we disagree with the sentiment it is important to note that prominent authors in that field---in which we are not experts---would disagree with the quantitative methods used in the research programme under discussion.

We therefore think it would be best to dampen pronouncements of novel paradigms and innovative N=1 analyses leading to fundamental shifts in the types of evidence we can now glean from adolescents' social media use and well-being. Because of the methodological and theoretical shortcomings detailed above, the research programme that is sometimes a "personalized media effects paradigm" [@valkenburgSocialMediaUse2021, p.74] and othertimes a "causal effect heterogeneity paradigm" [@valkenburgSocialMediaUse2022a, p.5] has not, and cannot if it proceeds with currently used methodology, meaningfully contributed to either.

# One last thing {-}

Throughout, we have been discussed *associations* between social media use and well-being. To be clear, the research communications emanating from this "idiographic [...] person-specific media *effects* paradigm" [@valkenburgSocialMediaUse2022, p.66, emphasis ours] consistently use causal language with little to no justification for it. This is especially salient when the same research programme is referred to as a "causal effect heterogeneity" approach [@valkenburgSocialMediaUse2022a, p.5]. Using lagged predictors, examining within-person associations, centering variables on observed or latent means, and other "advanced modeling technique[s]" [@beyensSocialMediaUse2021, p.3] might help, but fall far short from ensuring that the resulting quantitites represent causal effects. Examining causal effects is difficult, and doing so is made even more difficult if we are not clear about when we are and when we are not justified in doing so, and what assumptions must be satisfied to allow causal conclusions [@groszTabooExplicitCausal2020; @hernanCWordScientificEuphemisms2018].

@@

We have had fruitful back and forth with authors of the research programme whose work we are here commenting [@johannesHowShouldWe2021a; @valkenburgHowAssessVariation2022]. In addition to points raised in those discussions, here we wanted to make clear three points:

1. Quantifying population-level characteristics ought to be done using statistical models' population-level parameters.
2. Population-level characteristics do little to further the theoretical insights into any one individual's social media use and well-being associations.
3. Interpreting population-level estimates does not constitute idiographic research or a novel paradigm---especially not one that deals with causal effect.

Our intent is not to discourage publishing the kinds of work that we here criticize. Instead, we hope that our thoughts presented here would help clarify the ideas in those works that are critical to our current understanding of social media's roles---and digital technologies in general---in the well-being of human beings.

>>>>

---
title: Three objections to a novel person-specific paradigm in social media effects research
shorttitle: Three objections
leftheader: Three objections
author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes    # Define only one corresponding author
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - Conceptualization
      - Formal analysis
      - Software
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name: Niklas Johannes
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: niklas.johannes@oii.ox.ac.uk
    role:
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name: Andrew K. Przybylski
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: andy.przybylski@oii.ox.ac.uk
    role:
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
affiliation:
  - id: 1
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  A non-peer reviewed pre-print of this work is available at <psyarxiv>.
  All code supporting this manuscript is available at <https://github.com/digital-wellbeing/paradigm-comments>.
abstract: |
  The study of social media effects on psychological well-being has reached an impasse: Popular commentators confidently assert that social media are bad for users but research results are mixed and have had little practical impact. In response, one research group has proposed a path forward for the field that moves beyond studying population averages to find effects that are specific to individuals.

  Here, we outline three objections to that research agenda. On a methodological level, the key empirical results of this programme---proportions of the population of individuals with negative, null, and positive social media effects---are not appropriately estimated and reported. On a theoretical level, these results do little to advance our understanding of social media and its psychological implications. On a  paradigmatic level, this "personalized media effects paradigm" [@valkenburgSocialMediaUse2021, p.74] cannot inform inferences about individuals and therefore does not deliver what it claims.

  In this work we express our concern that this research approach may be contributing to confusing messaging to both societal stakeholders and scientists investigating how social media and well-being might be related. It is our sincere hope that describing these objections directly will prompt the field to work together in adopting better practices to ultimately develop a better understanding of well-being in the digital age.
keywords: social media, media effects, well-being, variation, paradigm
wordcount: "2,802"
bibliography: person-specific-paradigm.bib
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

@@

The main outcomes of the programme under question are "striking person-specific effects" [@valkenburgSocialMediaUse2022a, p.5]: Proportions of adolescents with negative, null, and positive associations between social media use and various well-being outcomes. We take these numerical results to be the key estimands because they are typically the numerical results reported in paper abstracts [e.g. @beyensSocialMediaUse2021; @valkenburgSocialMediaBrowsing2021]. Here, we argue that those numbers are inappropriately calculated and interpreted.

@@

We reproduced the authors' analysis in R using their openly shared data [@Beyens2021], but with three differences that merit mention here: First, we did not use robust standard errors; second, we were not able to reproduce the number of observations (authors reported 2,155, but the data we used had 2,210), and; third, we focused on the arguably more meaningful unstandardized coefficients in place of standardized ones [@baguleyStandardizedSimpleEffect2009; @cohenProblemUnitsCircumstance1999; @moellerWordStandardizationLongitudinal2015]. In addition, we were not sure if the predictors were latent-mean or observed-mean centered. None of these differences are material to the points we are about to illustrate, but explain why the numbers we report do not exactly reproduce the numbers reported in [@beyensEffectSocialMedia2020]. We present the key parameter estimates from this model in Table \@ref(tab:tab-coef).

@@

We find these numbers and their interpretations problematic for two reasons. First, they are reported without considering the uncertainties in the person-specific estimates. We think that a person-specific approach, if it intends to make inferences about specific individuals, ought to consider the certainty with which those individuals' characteristics (i.e. person-specific effects) are estimated. Similarly, from a heterogeneity-perspective, ignoring uncertainties and making inferences based on point estimates only will lead to distorted results. Thus, a more suitable approach would be to find person-specific estimates that are outside the null region with (e.g.) 95% confidence [@kruschkeBayesianNewStatistics2017].

To illustrate this point, after estimating the model we drew a caterpillar plot of $(\bar\beta_1 + \beta_{1\text{person}[j]})$ and $(\bar\beta_2 + \beta_{2\text{person}[j]})$ (Figure \@ref(fig:caterpillar) left and right, respectively.) We colored the person-specific estimates based on whether the posterior mean was outside or inside the null region. The authors used standardized effect size limits of (-0.1, 0.1) for the null region, but here we used a smallest effect size of interest (SESOI) of (-0.14, 0.14) on the raw scale---an approximate magnitude of change required to subjectively notice changes on well-being scales of this type [@anvariUsingAnchorbasedMethods2021]. Only 1 out of 63 individuals in this sample had a credibly non-null estimated association between passive social media use and well-being (estimates that are credibly outside the null region are filled in Figure \@ref(fig:caterpillar)). No other person's parameter was credibly outside the null region. In fact, they all indicated inconclusive, not null, results. We show these results numerically in the third column of Table \@ref(tab:tab-qoi). Ignoring the person-specific estimates' uncertainties can lead to numbers that do not represent the sample characteristics well, and serves to articifially inflate confidence in the results.

@@

x1 <- spread_draws(
  fit,
  b_active_c_w, b_passive_c_w,
  r_pid[pid, term] | term
) %>% 
  transmute(
    pid, .draw,
    Active = b_active_c_w + active_c_w,
    Passive = b_passive_c_w + passive_c_w
  ) %>% 
  pivot_longer(c(Active, Passive)) %>% 
  group_by(pid, name) %>% 
  mean_qi() %>% 
  mutate(
    zero = case_when(
      value >= 0.14 ~ "b",
      value <= -0.14 ~ "b",
      TRUE ~ "a"
    ),
    rope = case_when(
      .lower >= 0.14 ~ "Positive",
      .upper <= -0.14 ~ "Negative",
      .lower >= -0.14 & .upper <= 0.14 ~ "Null",
      TRUE ~ "Inconclusive"
    )
  ) %>% 
  arrange(name, value) %>% 
  mutate(pid = fct_inorder(str_c(pid, name)))
x1 %>% 
  ggplot(aes(value, pid, color = zero, shape = rope)) +
  scale_color_brewer(palette = "Paired") +
  scale_shape_manual(values = c(21, 19)) +
  geom_vline(xintercept = c(-.14, .14), lty = 2, size = .15) +
  geom_vline(xintercept = 0, lty = 1, size = .15) +
  scale_y_discrete(
    "Participant",
    expand = expansion(.025)
  ) +
  scale_x_continuous(
    "Estimated linear increase in well-being (1-7) as a\nfunction of a 10-minute increase in social media use",
    breaks = extended_breaks(7)
  ) +
  geom_linerange(
    size = .4,
    aes(xmin = .lower, xmax = .upper)
  ) +
  geom_point(fill = "white", stroke = 0.7, size = .9) +
  facet_wrap("name", scales = "free_y") +
  theme(
    axis.text.y = element_blank(), 
    axis.ticks.y = element_blank(),
    legend.position = "none"
  )
```

@@

For an illustration of calculating such population-level percentages, we again used an exemplar smallest effect size of interest (SESOI; [@anvariUsingAnchorbasedMethods2021]) of 0.14 on the raw scale. The results are shown in the fourth column of Table \@ref(tab:tab-qoi). Three lessons are apparent: One, the appropriately calculated percentages can be vastly different from those calculated from point estimates in Figure \@ref(fig:caterpillar). Two, calculating population-level quantities from the appropriate parameters allows quantifying uncertainty in them, as is shown in the credibility intervals of the percentages in Table \@ref(tab:tab-qoi). Three, there are no undecided person-specific parameters in the population, because the decision to accept or reject null hypotheses pertains to parameters at a different level of analysis. This last point highlights the confusion that results from how the programme under discussion here conflates studying heterogeneity (a feature of the population) with person-specific effects (features of individual people), and therefore does not meaningfully contribute to an understanding of either.

@@

In sum, for these two reasons---ignoring uncertainties and confusing levels of analyses---we argue that the percentages of social media associations in the population reported in (the abstracts of) an increasing number of manuscripts purporting to study heterogeneity and/or person-specific effects are misleading and lack critical context. We demonstrated how those numbers can be appropriately calculated, and then presented with appropriate indications of uncertainty.

@@

Even if we calculate these percentages correctly, the question of how this information can be used to develop and justify a new paradigm must be handled with care. We argue that doing so is difficult and simply reporting evidence of heterogeneity is insufficient. For one, the group interprets percentages that are not uniform as evidence that associations are not the same for everyone and we therefore cannot ignore heterogeneity. As observed previously [@johannesHowShouldWe2021a]: Variation is the norm, not the exception, and we consequently do not immediately know what to do with these findings because no preexisting theory of social media influence proposed otherwise. Instead of acknowledging that the heterogeneity in observed associations might reflect differential confounding of the actual causal effect or proposing clear interpretations of it, the authors assert that the field is on the cusp of a personalized "media *effects* paradigm" [@valkenburgSocialMediaUse2021, p.74, emphasis ours] akin to those theorized for medicine and education. We argue that merely observing that variation can be measured and might exist is an insufficient argument for the necessity of a new paradigm.

We agree that when heterogeneity is considerable, our substantive statements about the population must be qualified by this variation [@bolgerCausalProcessesPsychology2019]. But this is not the same sentiment that drives the argument that we are discussing here. The intent, apparently, is to develop a personalized understanding of social media *effects* for each individual; a truly idiographic goal [@valkenburgSocialMediaUse2021, p.74]. However, to date this goal is approached by extrapolating from inappropriately calculated population-level quantities; in this case percentages of individuals with associations in excess of some critical threshold. This fundamental tension between wants and haves has, we believe, led to a premature consideration of purportedly novel paradigms in a field that has not matured enough either methodologically or theoretically to consider addressing *causal* effects a manner that should attract the limited attention of policymakers and the general public [see e.g. @ijzermanUseCautionWhen2020].

As we have argued [@johannesHowShouldWe2021a], one way to resolve this tension is to use information about heterogeneity in considering meaningful moderators of social media associations [e.g. @bolgerCausalProcessesPsychology2019]. But this is standard practice in psychological research that routinely develops and refines theoretical models by moderating effects and associations with demographic and contextual variables. Another route, we believe espoused by this programme of research, is to move towards an idiographic (person-specific) research paradigm---a topic to which our next objection pertains.

@@

Throughout many papers on a "personalized media effects paradigm" [@valkenburgSocialMediaUse2021, p.74] the data analyses are framed as contributing, advancing, or constituting a novel idiographic media effects paradigm [@valkenburgSocialMediaUse2022, p.66]. The argument goes that since they are conducting N=1 analyses, the conclusions the authors draw are about individuals and in some cases these associations are framed as causal. But functions of ($\bar\beta_2$, $\sigma_{\beta_2}$) or poor stand-ins thereof (proportions of $\beta_2$), the main results reported in the manuscripts in question, are not idiographic in any meaningful sense of how that term is used in existing research traditions. We think that to truly conduct N=1 analyses in an idiographic manner, one must start with a wholly different epistemiological framing and do more than examine ranges of person-specific regression parameters.

In the context of multilevel models used in this body of work, idiographic research would refer to understanding each of 63 individuals' $\beta$s and explain what was behind their differences.[^1] It seems to us an inescapable conclusion---unless one wants to conduct high-quality qualitative interview and ethnographic work---that to study this heterogeneity further, we need to introduce more terms in our models to interact the associations of interest with meaningful contextual and person-level variables [@bolgerCausalProcessesPsychology2019]. These may then reduce the residual heterogeneity to such an extent that we may be excused for pronouncing that a meaningful between-person factor, such as a theory-informed moderator has been found, and we have learned something about individual differences in social media associations. Such conclusions and findings would be exceedingly difficult to come by through an idiographic-only approach, where individuals are "treated as holistic systems" [@howardVariableCenteredPersonCenteredPersonSpecific2018, p.849]. Repeating an earlier point, it is also important to not conflate person-specific analyses (which aim at analyzing a specific person) with effect heterogeneity (which encourages finding explanatory factors in the variation in effects).

[^1]: Prominent work in the idiographic research tradition actually argues against using shrinkage estimates for understanding individuals' characteristics, and as a consequence suggests that multilevel models are inappropriate tools for idiographic research [@molenaarManifestoPsychologyIdiographic2004; @molenaarNewPersonSpecificParadigm2009]. While we disagree with that sentiment, it is important to note that prominent authors in the field of idiographic research---in which we are not experts---would disagree with the quantitative methods used in the research programme under discussion.

Throughout, we have discussed *associations* between social media use and well-being. To be clear, the research communications emanating from this "idiographic [...] person-specific media *effects* paradigm" [@valkenburgSocialMediaUse2022, p.66, emphasis ours] consistently use causal language with little to no justification for it. This is especially salient when the same research programme is referred to as a "causal effect heterogeneity" approach [@valkenburgSocialMediaUse2022a, p.5]. Using lagged predictors, examining within-person associations, centering variables on observed or latent means, and other "advanced modeling technique[s]" [@beyensSocialMediaUse2021, p.3] might help, but fall far short from ensuring that the resulting quantities represent causal effects. Examining causal effects is difficult and doing so is made even more difficult if we are not clear about when we are and when we are not justified in making causal conclusions [@groszTabooExplicitCausal2020; @hernanCWordScientificEuphemisms2018].

We therefore think it would be best for social scientists to proceed cautiously before making pronouncements of novel paradigms and innovative N=1 analyses leading to fundamental shifts in the types of evidence we can now glean from adolescents' social media use and well-being. Because of the methodological and theoretical shortcomings detailed here, the research programme that is sometimes a "personalized media effects paradigm" [@valkenburgSocialMediaUse2021, p.74] and othertimes a "causal effect heterogeneity paradigm" [@valkenburgSocialMediaUse2022a, p.5] has not, and cannot if it proceeds with currently used methodology, meaningfully contribute to either.

@@

With all of this in mind, we underscore the valuable and collegial exchanges we have had with the authors whose work we are here critiquing [@johannesHowShouldWe2021a; @valkenburgHowAssessVariation2022]. The stakes for understanding well-being in the digital age are simply too high for personal acrimony or ideological fiefdoms. To break the current impasse, three simple points should be widely acknowledged and integrated into our collective research practices:

1. Quantifying population-level characteristics ought to be done using statistical models' population-level parameters.
2. Population-level characteristics do little to further theoretical insights into any one individual's social media use and well-being associations.
3. Interpreting population-level estimates does not constitute idiographic research or a novel paradigm---especially not one that deals with causal effect.

We also emphasize that our intent is not to discourage publishing the kinds of work that we critique. Instead, we hope that our arguments and worked examples help clarify the ideas under development and bring the outstanding challenges we face into a sharper relief. This and related work is critical to our current understanding of how social media---and digital technologies in general---might influence, for good or ill, our collective well-being.
